**The Role of Interoception and Theory of Mind in Deception**

### 2022-10-04 1_Measures.Rmd
update

## Theory of Mind / Empathy

@@

```{r warning=FALSE}
df |> 
  select(Participant, Confidence, RT, HeartRate) |> 
  tidyr::pivot_longer(-Participant) |> 
  ggplot(aes(x=Participant, y=value)) +
  geom_violin(aes(fill=name), color="white", alpha=0.5) +
  geom_jitter(aes(color=name), width = 0.25, height=0, shape="+", size=2) +
  facet_wrap(~name, scales="free", nrow=3) +
  guides(fill="none", color="none")

df$Confidence[df$Participant %in% c("S9", "S29")] <- NA # Extreme responses
df$HeartRate[df$Participant == "S30"] <- NA # Extreme values
df$RT[df$Participant == "S13"] <- NA # Slower than the others
df$RT[df$RT > 8.25] <- NA # Extreme RT values 
```

Percentage of Confidence data removed: `r sum(is.na(df$Confidence)) / nrow(df) * 100` %  
Percentage of RT data removed: `r sum(is.na(df$RT)) / nrow(df) * 100` %  
Percentage of Heart Rate data removed: `r sum(is.na(df$HeartRate)) / nrow(df) * 100` %

@@

```{r warning=FALSE}
df <- df |> 
  # Remove outlier trials
  group_by(Participant) |> 
  mutate(Outliers_RT = as.logical(performance::check_outliers(RT, method = "zscore", threshold = qnorm(0.9999))),
         Outliers_Physio = as.logical(performance::check_outliers(HeartRate, method = "zscore", threshold = qnorm(0.9999)))) |> 
  ungroup()
```

@@

>>>>

## Outcomes

```{r message=FALSE}
p1 <- estimate_density(df$Confidence, at=df$Participant, method = "kernSmooth") |> 
  ggplot(aes(x=x, y=y)) +
  geom_line(aes(color = Group)) + 
  scale_x_continuous(labels = scales::percent, expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(x = "Confidence", y = "") +
  scale_colour_flat_d(guide="none")

p2 <- estimate_density(df$RT, at=df$Participant, method = "kernSmooth") |> 
  ggplot(aes(x=x, y=y)) +
  geom_line(aes(color = Group)) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(x = "RT (s)", y = "") +
  scale_colour_viridis_d(guide="none")

p3 <- estimate_density(filter(df, !is.na(HeartRate)), select="HeartRate", at="Participant", method = "kernSmooth") |> 
  ggplot(aes(x=x, y=y)) +
  geom_line(aes(color = Participant)) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(x = "Heart Rate (bpm)", y = "") +
  scale_colour_pizza_d(guide="none")

p1 / p2 / p3 + plot_annotation(title = "Distribution of each participant")
```
## Theory of Mind / Empathy

@@

```{r warning=FALSE}
df |> 
  select(Participant, Confidence, RT, HeartRate) |> 
  tidyr::pivot_longer(-Participant) |> 
  ggplot(aes(x=Participant, y=value)) +
  geom_violin(aes(fill=name), color="white", alpha=0.5) +
  geom_jitter(aes(color=name), width = 0.25, height=0, shape="+", size=2) +
  facet_wrap(~name, scales="free", nrow=3) +
  guides(fill="none", color="none")
```

@@

@@

## Inter-Measures Correlation {.tabset}

```{r message=FALSE, warning=FALSE}
dfsub <- df |> 
  select(Participant, 
         starts_with("YONI_"), 
         starts_with("BES_"),
         starts_with("HCT_"),
         starts_with("HTT_"),
         starts_with("MAIA_"),
         starts_with("LIE_")) |> 
  group_by(Participant) |> 
  summarise_all(mean)
```

### Theory of Mind / Empathy

```{r message=FALSE, warning=FALSE}
r <- correlation(select(dfsub, starts_with("YONI_")),
                 select(dfsub, starts_with("BES_")), 
                 p_adjust = "none")

summary(r) |> 
  plot() 
```

### Interoception

```{r message=FALSE, warning=FALSE}
# Leave out HTT
# r <- correlation(select(dfsub, starts_with("HTT_")),
#                  select(dfsub, starts_with("HCT_")), 
#                  p_adjust = "none")
# 
# summary(r) |> 
#   plot()
```

```{r message=FALSE, warning=FALSE}
r <- correlation(select(dfsub, starts_with("MAIA_")),
                 select(dfsub, starts_with("HCT_")), 
                        #starts_with("HTT_")), 
                 p_adjust = "none")

summary(r) |> 
  plot()
```

### ToM and Interoception

```{r message=FALSE, warning=FALSE}
r <- correlation(select(dfsub, starts_with(c("MAIA_", "HCT_"))),
                 select(dfsub, starts_with(c("YONI_", "BES_"))), 
                 p_adjust = "none")

summary(r) |> 
  plot() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
```

### Deception Task and LIE Scale

```{r message=FALSE, warning=FALSE}
r <- df |> 
  select(Participant, Answer, Confidence, RT, HeartRate) |> 
  group_by(Participant, Answer) |> 
  summarise_all(mean, na.rm=TRUE) |> 
  tidyr::pivot_wider(names_from = "Answer", values_from = c("Confidence", "RT", "HeartRate")) |> 
  ungroup() |> 
  select(-Participant) |> 
  correlation(select(dfsub, starts_with("LIE_")), p_adjust = "none")

summary(r) |> 
  plot()
```

### Confidence and RT

- When lying, the faster they answer, the more confident they are.

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ RT * Answer + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

parameters::parameters(model, effects = "fixed")
```

```{r message=FALSE, warning=FALSE}
modelbased::estimate_slopes(model, trend = "RT", at = "Answer")
```

```{r message=FALSE, warning=FALSE}
estimate_relation(model, at = c("RT", "Answer")) |> 
  plot(length = 50, point = list(alpha = 0.3, size = 3.5)) 
```

### Confidence and Heart Rate

- More confidence in truths is associated with higher heart rate.

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ HeartRate * Answer + (1|Participant) + (1|Item), 
                 data = df, family = beta_family()) # warning can be ignored

parameters::parameters(model, effects = "fixed")
```

```{r message=FALSE, warning=FALSE}
modelbased::estimate_slopes(model, trend = "HeartRate", at = "Answer")
```

```{r message=FALSE, warning=FALSE}
estimate_relation(model, at = c("HeartRate", "Answer")) |> 
  plot(length = 50, point = list(alpha = 0.3, size = 3.5)) 
```

### RT and Heart Rate

- No relationship.

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ HeartRate * Answer + (1|Participant) + (1|Item), 
                 data = df)

parameters::parameters(model, effects = "fixed")
```

```{r message=FALSE, warning=FALSE}
estimate_relation(model, at = c("HeartRate", "Answer")) |> 
  plot(length = 50, point = list(alpha = 0.3, size = 3.5)) 
```

### 2022-10-04 2_ManipulationChecks.Rmd
added interpretations
update

## Inter-Measures Correlation {.tabset}

```{r message=FALSE, warning=FALSE}
dfsub <- df |> 
  select(Participant, 
         starts_with("YONI_"), 
         starts_with("BES_"),
         starts_with("HCT_"),
         starts_with("HTT_"),
         starts_with("MAIA_"),
         starts_with("LIE_")) |> 
  group_by(Participant) |> 
  summarise_all(mean)
```

### Theory of Mind / Empathy

```{r message=FALSE, warning=FALSE}
r <- correlation(select(dfsub, starts_with("YONI_")),
                 select(dfsub, starts_with("BES_")), 
                 p_adjust = "none")

summary(r) |> 
  plot() 
```

### Interoception

```{r message=FALSE, warning=FALSE}
# Leave out HTT
# r <- correlation(select(dfsub, starts_with("HTT_")),
#                  select(dfsub, starts_with("HCT_")), 
#                  p_adjust = "none")
# 
# summary(r) |> 
#   plot()
```

```{r message=FALSE, warning=FALSE}
r <- correlation(select(dfsub, starts_with("MAIA_")),
                 select(dfsub, starts_with("HCT_")), 
                        #starts_with("HTT_")), 
                 p_adjust = "none")

summary(r) |> 
  plot()
```

### ToM and Interoception

```{r message=FALSE, warning=FALSE}
r <- correlation(select(dfsub, starts_with(c("MAIA_", "HCT_"))),
                 select(dfsub, starts_with(c("YONI_", "BES_"))), 
                 p_adjust = "none")

summary(r) |> 
  plot() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
```

### Deception Task and LIE Scale

```{r message=FALSE, warning=FALSE}
r <- df |> 
  select(Participant, Answer, Confidence, RT, HeartRate) |> 
  group_by(Participant, Answer) |> 
  summarise_all(mean, na.rm=TRUE) |> 
  tidyr::pivot_wider(names_from = "Answer", values_from = c("Confidence", "RT", "HeartRate")) |> 
  ungroup() |> 
  select(-Participant) |> 
  correlation(select(dfsub, starts_with("LIE_")), p_adjust = "none")

summary(r) |> 
  plot()
```

### Confidence and RT

- When lying, the faster they answer, the more confident they are.

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ RT * Answer + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

parameters::parameters(model, effects = "fixed")
```

```{r message=FALSE, warning=FALSE}
modelbased::estimate_slopes(model, trend = "RT", at = "Answer")
```

```{r message=FALSE, warning=FALSE}
estimate_relation(model, at = c("RT", "Answer")) |> 
  plot(length = 50, point = list(alpha = 0.3, size = 3.5)) 
```

### Confidence and Heart Rate

- More confidence in truths is associated with higher heart rate.

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ HeartRate * Answer + (1|Participant) + (1|Item), 
                 data = df, family = beta_family()) # warning can be ignored

parameters::parameters(model, effects = "fixed")
```

```{r message=FALSE, warning=FALSE}
modelbased::estimate_slopes(model, trend = "HeartRate", at = "Answer")
```

```{r message=FALSE, warning=FALSE}
estimate_relation(model, at = c("HeartRate", "Answer")) |> 
  plot(length = 50, point = list(alpha = 0.3, size = 3.5)) 
```

### RT and Heart Rate

- No relationship.

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ HeartRate * Answer + (1|Participant) + (1|Item), 
                 data = df)

parameters::parameters(model, effects = "fixed")
```

```{r message=FALSE, warning=FALSE}
estimate_relation(model, at = c("HeartRate", "Answer")) |> 
  plot(length = 50, point = list(alpha = 0.3, size = 3.5)) 
```

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ Answer * Phrasing + (1|Participant) + (1|Item), 
                 data = df)

parameters::parameters(model, effects = "fixed")
```

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ Answer * Phrasing + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

parameters::parameters(model, effects = "fixed")
```

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(HeartRate ~ Answer * Phrasing + (1|Participant) + (1|Item), 
                 data = df)

parameters::parameters(model, effects = "fixed")
```

@@

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ Answer * Condition + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

parameters::parameters(model, effects = "fixed")
```

@@

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ Answer * Condition + (1|Participant) + (1|Item), 
                 data = df)

parameters::parameters(model, effects = "fixed")
```

@@

- Higher heart rate in lies vs. truths, and higher heart rate in interrogation condition vs. polygraph.
- No interaction.

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(HeartRate ~ Answer * Condition + (1|Participant) + (1|Item), 
                 data = df)

parameters::parameters(model, effects = "fixed")
```

@@

>>>>

@@

```{r message=FALSE, warning=FALSE}
# Prior: plot(seq(-5, 5, length.out=100), dstudent_t(seq(-5, 5, length.out=100), 1, 0, 1), "l")

model <- brms::brm(Confidence ~ Answer * Condition + (1|Participant) + (1|Item), 
                   data = df, family = "beta", seed=3, refresh=0,
                   prior = set_prior("student_t(1, 0, 1)", class = "b"))

show_parameters(model)
```

@@

```{r message=FALSE, warning=FALSE}
# Prior: plot(seq(-10, 10, length.out=100), dstudent_t(seq(-10, 10, length.out=100), 1, 0, 3), "l")

model <- brms::brm(RT ~ Answer * Condition + (1|Participant) + (1|Item),
                   data = df, seed=3, refresh=0,
                   prior = set_prior("student_t(1, 0, 3)", class = "b"))

show_parameters(model)
```

@@

- Higher heart rate in lies vs. truths.
- Higher heart rate in interrogation condition vs. polygraph: presence of another person causes heightened physiological arousals.
- No interaction.

```{r message=FALSE, warning=FALSE}
# Prior: plot(seq(-30, 30, length.out=100), dstudent_t(seq(-30,30, length.out=100), 1, 0, 8), "l")
model <- brms::brm(HeartRate ~ Answer * Condition + (1|Participant) + (1|Item),
                   data = df, seed=3, refresh=0,
                   prior = set_prior("student_t(1, 0, 8)", class = "b"))

show_parameters(model)
```

@@

```{r message=FALSE, warning=FALSE}
# Prior: plot(seq(-2, 2, length.out=100), dstudent_t(seq(-2, 2, length.out=100), 1, 0, 1), "l")

model <- brms::brm(Confidence ~ Answer * Phrasing + (1|Participant) + (1|Item), 
                   data = df, family = "beta", seed=3, refresh=0,
                   prior = set_prior("student_t(1, 0, 1)", class = "b"))

show_parameters(model)
```

```{r message=FALSE, warning=FALSE}
# Prior: plot(seq(-10, 10, length.out=100), dstudent_t(seq(-10, 10, length.out=100), 1, 0, 3), "l")

model <- brms::brm(RT ~ Answer * Phrasing + (1|Participant) + (1|Item),
                   data = df, seed=3, refresh=0,
                   prior = set_prior("student_t(1, 0, 3)", class = "b"))

show_parameters(model)
```

```{r message=FALSE, warning=FALSE}
# Prior: plot(seq(-50, 50, length.out=100), dstudent_t(seq(-50, 50, length.out=100), 1, 0, 8), "l")
model <- brms::brm(HeartRate ~ Answer * Phrasing + (1|Participant) + (1|Item),
                   data = df, seed=3, refresh=0,
                   prior = set_prior("student_t(1, 0, 8)", class = "b"))

show_parameters(model)
```

### 2022-10-04 3_ToM.Rmd
update

- When instructed to lie, the decrease in confidence in participants with higher yoni score is less in social than polygraph condition.

### Total Score

#### Confidence

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ Answer / (Condition * YONI_Total) + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

get_parameters <- function(model) {
  # Parameters
  params <- parameters::parameters(model, effects = "fixed") 
  # Marginal effects
  at <- c("Answer", "Condition")
  trend <- insight::find_predictors(model)$conditional
  trend <- trend[!trend %in% at]
  marg <- modelbased::estimate_slopes(model, trend = trend, at = at)
  # Output
  list(params = params, marginal_effects = marg)
}

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
plot_effect <- function(model, results, var = "YONI_Total", outcome = "Confidence") {
  data <- df |> 
    group_by(Participant, Answer, Condition) |> 
    summarise({{var}} := mean(.data[[var]], na.rm = TRUE),
              SD = sd(.data[[outcome]], na.rm = TRUE),
              {{outcome}} := mean(.data[[outcome]], na.rm = TRUE),
              CI_low = .data[[outcome]] - SD / 2,
              CI_high = .data[[outcome]] + SD / 2)

  link_data <- estimate_relation(model, at = c("Condition", var, "Answer"), length = 30)
  range_x <- diff(range(data[[var]]))

  annot <- results$marginal_effects  
  annot$Label <- insight::format_p(annot$p, stars_only = TRUE)
  annot$x <- mean(range(data[[var]]))
  annot$x <- ifelse(annot$Condition == "Polygraph", 
                    annot$x - 0.05 * range_x, 
                    annot$x + 0.05 * range_x)
  annot$y <- max(data[[outcome]], na.rm=TRUE) - 0.01 * diff(range(data[[outcome]], na.rm=TRUE))

  p <- ggplot(link_data, aes_string(x = var, y = "Predicted")) +
    geom_pointrange(data = data, 
                    aes_string(y = outcome, 
                               color = "Condition", 
                               ymin = "CI_low", 
                               ymax = "CI_high"), 
                    position = position_dodge(width = 0.02 * range_x)) +
    geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Condition), alpha = 0.33) + 
    geom_line(aes(color = Condition)) +
    geom_text(data=annot, aes(x = x, y = y, label = Label, color = Condition), 
              size = 8, show.legend = FALSE) +
    labs(y = ifelse(outcome == "RT", "Reaction Time (s)", ifelse(outcome == "HeartRate", "Heart Rate (bpm)", "Confidence")), 
         x = paste0(stringr::str_replace(var, "_", " ("), ")")) +
    scale_color_manual(values = c("Polygraph" = "#FF5722", "Social" = "#2196F3")) +
    scale_fill_manual(values = c("Polygraph" = "#FF5722", "Social" = "#2196F3")) + 
    facet_wrap(~Answer)

  # Narrow y range
  if(outcome == "Confidence") {
    p <- p +
      coord_cartesian(ylim = c(0, 1)) +
      scale_y_continuous(expand=expansion(c(0, 0))) 
  }
  p
}

p_conf_yoni_total <- plot_effect(model, results, var = "YONI_Total", outcome = "Confidence")
```

#### RT

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ Answer / (Condition * YONI_Total) + (1|Participant) + (1|Item), 
                 data = df)

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
p_rt_yoni_total <- plot_effect(model, results, var = "YONI_Total", outcome = "RT")
# p_rt_yoni_total
```

#### Heart Rate

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(HeartRate ~ Answer / (Condition * YONI_Total) + (1|Participant), 
                 data = df)

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
p_hr_yoni_total <- plot_effect(model, results, var = "YONI_Total", outcome = "HeartRate")
# p_hr_yoni_total
```

### Cognitive Theory of Mind

#### Confidence

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ Answer / (Condition * YONI_Cognitive) + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
p_conf_yoni_cognitive <- plot_effect(model, results, var = "YONI_Cognitive", outcome = "Confidence")
# p_conf_yoni_cognitive
```

#### RT

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ Answer / (Condition * YONI_Cognitive) + (1|Participant) + (1|Item), 
                 data = df)

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
p_rt_yoni_cognitive <- plot_effect(model, results, var = "YONI_Cognitive", outcome = "RT")
# p_rt_yoni_cognitive
```

#### Heart Rate

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(HeartRate ~ Answer / (Condition * YONI_Cognitive) + (1|Participant), 
                 data = df)

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
p_hr_yoni_cognitive <- plot_effect(model, results, var = "YONI_Cognitive", outcome = "HeartRate")
# p_hr_yoni_cognitive
```

### Affective Theory of Mind

#### Confidence

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ Answer / (Condition * YONI_Affective) + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
p_conf_yoni_affective <- plot_effect(model, results, var = "YONI_Affective", outcome = "Confidence")
# p_conf_yoni_affective
```

#### RT

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ Answer / (Condition * YONI_Affective) + (1|Participant) + (1|Item), 
                 data = df)

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
p_rt_yoni_affective <- plot_effect(model, results, var = "YONI_Affective", outcome = "RT")
# p_rt_yoni_affective
```

#### Heart Rate

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(HeartRate ~ Answer / (Condition * YONI_Affective) + (1|Participant), 
                 data = df)

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
p_hr_yoni_affective <- plot_effect(model, results, var = "YONI_Affective", outcome = "HeartRate")
# p_hr_yoni_affective
```

### Physical Theory of Mind

#### Confidence

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ Answer / (Condition * YONI_Physical) + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
p_conf_yoni_physical <- plot_effect(model, results, var = "YONI_Physical", outcome = "Confidence")
# p_conf_yoni_physical
```

#### RT

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ Answer / (Condition * YONI_Physical) + (1|Participant) + (1|Item), 
                 data = df)

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
p_rt_yoni_physical <- plot_effect(model, results, var = "YONI_Physical", outcome = "RT")
# p_rt_yoni_physical
```

#### Heart Rate

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(HeartRate ~ Answer / (Condition * YONI_Physical) + (1|Participant), 
                 data = df)

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
p_hr_yoni_physical <- plot_effect(model, results, var = "YONI_Physical", outcome = "HeartRate")
# p_hr_yoni_physical
```

@@

```{r message=FALSE, warning=FALSE}
get_correlation <- function(var = "YONI_", var2 = "LIE_") {
  r <- correlation(select(dfsub, starts_with(var2)),
                 select(dfsub, starts_with(var)), 
                 p_adjust = "none") |> 
  mutate(Parameter1 = paste0(str_replace(Parameter1, "_", " ("), ")"),
         Parameter2 = paste0(str_replace(Parameter2, "_", " ("), ")"))

  p <- summary(r) |> 
    plot() +
    theme_minimal()
  list(r = r, plot = p)
}

r <- get_correlation(var = "YONI_")
r$plot
```

### Summary

```{r message=FALSE, warning=FALSE, fig.height=figheight*3, fig.width=figwidth*1.5}
p_conf_yoni_total / 
  p_conf_yoni_cognitive / 
  p_conf_yoni_affective / 
  p_conf_yoni_physical +
  patchwork::plot_annotation(title = "Theory of Mind", theme = theme(plot.title = element_text(hjust = 0.5)))

p_rt_yoni_total / 
  p_rt_yoni_cognitive / 
  p_rt_yoni_affective / 
  p_rt_yoni_physical +
  patchwork::plot_annotation(title = "Theory of Mind", theme = theme(plot.title = element_text(hjust = 0.5)))

p_hr_yoni_total / 
  p_hr_yoni_cognitive / 
  p_hr_yoni_affective / 
  p_hr_yoni_physical +
  patchwork::plot_annotation(title = "Theory of Mind", theme = theme(plot.title = element_text(hjust = 0.5)))
```

@@

### Total Score

#### Confidence

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ Answer / (Condition * BES_Total) + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
p_conf_bes_total <- plot_effect(model, results, var = "BES_Total", outcome = "Confidence")
# p_conf_bes_total
```

#### RT

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ Answer / (Condition * BES_Total) + (1|Participant) + (1|Item), 
                 data = df)

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
p_rt_bes_total <- plot_effect(model, results, var = "BES_Total", outcome = "RT")
# p_rt_bes_total
```

#### Heart Rate

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(HeartRate ~ Answer / (Condition * BES_Total) + (1|Participant), 
                 data = df)

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
p_hr_bes_total <- plot_effect(model, results, var = "BES_Total", outcome = "HeartRate")
# p_hr_bes_total
```

### Cognitive Empathy

#### Confidence

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ Answer / (Condition * BES_Cognitive) + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
p_conf_bes_cognitive <- plot_effect(model, results, var = "BES_Cognitive", outcome = "Confidence")
# p_conf_bes_cognitive
```

#### RT

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ Answer / (Condition * BES_Cognitive) + (1|Participant) + (1|Item), 
                 data = df)

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
p_rt_bes_cognitive <- plot_effect(model, results, var = "BES_Cognitive", outcome = "RT")
# p_rt_bes_cognitive
```

#### Heart Rate

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(HeartRate ~ Answer / (Condition * BES_Cognitive) + (1|Participant), 
                 data = df)

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
p_hr_bes_cognitive <- plot_effect(model, results, var = "BES_Cognitive", outcome = "HeartRate")
# p_hr_bes_cognitive
```

### Affective Empathy

#### Confidence

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(Confidence ~ Answer / (Condition * BES_Affective) + (1|Participant) + (1|Item), 
                 data = df, family = beta_family())

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
p_conf_bes_affective <- plot_effect(model, results, var = "BES_Affective", outcome = "Confidence")
# p_conf_bes_affective
```

#### RT

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(RT ~ Answer / (Condition * BES_Affective) + (1|Participant) + (1|Item), 
                 data = df)

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
p_rt_bes_affective <- plot_effect(model, results, var = "BES_Affective", outcome = "RT")
# p_rt_bes_affective
```

#### Heart Rate

```{r message=FALSE, warning=FALSE}
model <- glmmTMB(HeartRate ~ Answer / (Condition * BES_Affective) + (1|Participant), 
                 data = df)

results <- get_parameters(model)
results$params
results$marginal_effects
```

```{r message=FALSE, warning=FALSE}
p_hr_bes_affective <- plot_effect(model, results, var = "BES_Affective", outcome = "HeartRate")
# p_hr_bes_affective
```

@@

```{r message=FALSE, warning=FALSE}
r <- get_correlation(var = "BES_")
r$plot
```

### Summary

```{r message=FALSE, warning=FALSE, fig.height=figheight*3, fig.width=figwidth*1.5}
p_conf_bes_total / 
  p_conf_bes_cognitive / 
  p_conf_bes_affective +
  patchwork::plot_annotation(title = "Empathy", theme = theme(plot.title = element_text(hjust = 0.5)))

p_rt_bes_total / 
  p_rt_bes_cognitive / 
  p_rt_bes_affective +
  patchwork::plot_annotation(title = "Empathy", theme = theme(plot.title = element_text(hjust = 0.5)))

p_hr_bes_total / 
  p_hr_bes_cognitive / 
  p_hr_bes_affective +
  patchwork::plot_annotation(title = "Empathy", theme = theme(plot.title = element_text(hjust = 0.5)))
```

>>>>

- Confidence: effect in total, cognitive and physical.
- RT: effect in cognitive only.
- Heart rate: no effect.

### Confidence

```{r message=FALSE, warning=FALSE}
results <- data.frame()
for (var in c("YONI_Total", "YONI_Cognitive", "YONI_Affective", "YONI_Physical")) {
  model <- glmmTMB(as.formula(paste0("Confidence ~ Answer / (Condition / ", 
                                     var, 
                                     ") + (1|Participant) + (1|Item)")), 
                   data = df, 
                   family = beta_family())

  results <- parameters::parameters(model, effects = "fixed", keep=var) |> 
    mutate(Parameter = str_remove(Parameter, "Answer|Condition")) |> 
    separate(Parameter, sep=":", into = c("Answer", "Condition", "Variable")) |> 
    data_relocate(select="Variable", before=1) |> 
    rbind(results)
}

display(results, stars=TRUE)
```

### RT

```{r message=FALSE, warning=FALSE}
results <- data.frame()
for (var in c("YONI_Total", "YONI_Cognitive", "YONI_Affective", "YONI_Physical")) {
  model <- glmmTMB(as.formula(paste0("RT ~ Answer / (Condition / ", 
                                     var, 
                                     ") + (1|Participant) + (1|Item)")), 
                   data = df)

  results <- parameters::parameters(model, effects = "fixed", keep=var) |> 
    mutate(Parameter = str_remove(Parameter, "Answer|Condition")) |> 
    separate(Parameter, sep=":", into = c("Answer", "Condition", "Variable")) |> 
    data_relocate(select="Variable", before=1) |> 
    rbind(results)
}

display(results, stars=TRUE)
```

### Heart Rate

```{r message=FALSE, warning=FALSE}
results <- data.frame()
for (var in c("YONI_Total", "YONI_Cognitive", "YONI_Affective", "YONI_Physical")) {
  model <- glmmTMB(as.formula(paste0("HeartRate ~ Answer / (Condition / ", 
                                     var, 
                                     ") + (1|Participant) + (1|Item)")), 
                   data = df)

  results <- parameters::parameters(model, effects = "fixed", keep=var) |> 
    mutate(Parameter = str_remove(Parameter, "Answer|Condition")) |> 
    separate(Parameter, sep=":", into = c("Answer", "Condition", "Variable")) |> 
    data_relocate(select="Variable", before=1) |> 
    rbind(results)
}

display(results, stars=TRUE)
```

@@

```{r message=FALSE, warning=FALSE}
dfsub <- df |> 
  select(Participant, 
         starts_with("LIE_"), 
         starts_with("YONI_")) |> 
  group_by(Participant) |> 
  summarise_all(mean)

correlation(select(dfsub, starts_with("LIE_")), select(dfsub, starts_with("YONI_")), p_adjust = "none")
```

@@

- Confidence: effect in all.
- RT: no effect.
- Heart rate: effect in all.

### Confidence

```{r message=FALSE, warning=FALSE}
results <- data.frame()
for (var in c("BES_Total", "BES_Cognitive", "BES_Affective")) {
  model <- glmmTMB(as.formula(paste0("Confidence ~ Answer / (Condition / ", 
                                     var, 
                                     ") + (1|Participant) + (1|Item)")), 
                   data = df, 
                   family = beta_family())

  results <- parameters::parameters(model, effects = "fixed", keep=var) |> 
    mutate(Parameter = str_remove(Parameter, "Answer|Condition")) |> 
    separate(Parameter, sep=":", into = c("Answer", "Condition", "Variable")) |> 
    data_relocate(select="Variable", before=1) |> 
    rbind(results)
}

display(results, stars=TRUE)
```

### RT

```{r message=FALSE, warning=FALSE}
results <- data.frame()
for (var in c("BES_Total", "BES_Cognitive", "BES_Affective")) {
  model <- glmmTMB(as.formula(paste0("RT ~ Answer / (Condition / ", 
                                     var, 
                                     ") + (1|Participant) + (1|Item)")), 
                   data = df)

  results <- parameters::parameters(model, effects = "fixed", keep=var) |> 
    mutate(Parameter = str_remove(Parameter, "Answer|Condition")) |> 
    separate(Parameter, sep=":", into = c("Answer", "Condition", "Variable")) |> 
    data_relocate(select="Variable", before=1) |> 
    rbind(results)
}

display(results, stars=TRUE)
```

### Heart Rate

```{r message=FALSE, warning=FALSE}
results <- data.frame()
for (var in c("BES_Total", "BES_Cognitive", "BES_Affective")) {
  model <- glmmTMB(as.formula(paste0("HeartRate ~ Answer / (Condition / ", 
                                     var, 
                                     ") + (1|Participant) + (1|Item)")), 
                   data = df)

  results <- parameters::parameters(model, effects = "fixed", keep=var) |> 
    mutate(Parameter = str_remove(Parameter, "Answer|Condition")) |> 
    separate(Parameter, sep=":", into = c("Answer", "Condition", "Variable")) |> 
    data_relocate(select="Variable", before=1) |> 
    rbind(results)
}

display(results, stars=TRUE)
```

@@

```{r message=FALSE, warning=FALSE}
dfsub <- df |> 
  select(Participant, 
         starts_with("LIE_"), 
         starts_with("BES_")) |> 
  group_by(Participant) |> 
  summarise_all(mean)

correlation(select(dfsub, starts_with("LIE_")), select(dfsub, starts_with("BES_")), p_adjust = "none")
```
